A generalized definition of multidimensional item response theory parameters

### 2024-09-06 output/Main_text.Rmd
Corrects transformation matrix
In the graphical representation algorithm, the latent space transformation matrix is incorrectly referenced, instead of its transpose inverse (i.e. the transformation matrix in the test space)

1. Compute the rectangular coordinates
   $`r ORIGIN_ITEM_ORTH`$ and $`r END_ITEM_ORTH`$ by pre-multiplying
   $`r ORIGIN_ITEM_BASIS`$ and $`r END_ITEM_BASIS`$, respectively, by
   the transformation matrix $`r TRANSFORM_MATRIX`$
   ($`r ORIGIN_TRANSF_EQ`$; $`r END_TRANSF_EQ`$).

@@

Finally, we must also warn against generalizing these results
to other IRT models without further consideration.
First, we have only considered the case of dichotomous items,
whereas non-cognitive applications often (and sometimes cognitive ones as well)
require modeling several response categories.
Although proposals such as the graded-scale [@samejima_estimation_1968] and
the nominal response [@bock_estimating_1972] model are closely related to
the 2-parameter logistic model, it would be hasty to assume that these
parameters generalize in any way to
the multidimensional versions of those models without a formal proof.
The same can be said from the multidimensional parameters of other models
for dichotomous items different from the `r MODEL_ACRONYM` model.
We expect this work to help set the foundations for investigating those
generalizations.
Hopefully, this will contribute to a better understanding
of the underlying multidimensional measurement theory, its implications,
and its interpretation.

>>>>

1. Compute the rectangular coordinates
   $`r ORIGIN_ITEM_ORTH`$ and $`r END_ITEM_ORTH`$ by pre-multiplying
   $`r ORIGIN_ITEM_BASIS`$ and $`r END_ITEM_BASIS`$, respectively, by
   the transformation matrix $`r TRANSFORM_MATRIX_TRANSP_INV`$
   ($`r ORIGIN_TRANSF_EQ`$; $`r END_TRANSF_EQ`$).

@@

Finally, we must also warn against generalizing these results
to other IRT models without further consideration.
First, we have only considered the case of dichotomous items,
whereas non-cognitive applications often (and sometimes cognitive ones as well)
require modeling several response categories.
Although proposals such as the graded-scale [@samejima_estimation_1968] and
the nominal response [@bock_estimating_1972] models are closely related to
the 2-parameter logistic model, it would be hasty to assume that these
parameters generalize in any way to
the multidimensional versions of those models without a formal proof.
The same can be said from the multidimensional parameters of other models
for dichotomous items different from the `r MODEL_ACRONYM` model.
We expect this work to help set the foundations for investigating those
generalizations.
Hopefully, this will contribute to a better understanding
of the underlying multidimensional measurement theory, its implications,
and its interpretation.
